Exploring probability distributions for bivariate temporal granularities

### 2020-01-30 main.Rmd
header change
minor changes and names of sub headers in smsrt meter

### Mapping

@@

<!-- # how data looks -->
Smart meters provide large quantities of measurements on energy usage for households across Australia. One of the customer trial [@smart-meter] conducted as part of the Smart Grid Smart City (SGSC) project (2010-2014) in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption in `general_supply_kwh` in every half hour from February 2012 to March 2014. \ref{fig:smart-meter} shows the data structure of the available data. It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units. The idea here is to show how looking at the energy consumption across different cyclic granularities together can help identify different behavioral patterns and identify the extreme and regular households.

@@

smart_meter
```

@@

**gravitas** R package [@R-gravitas] is used to facilitate the systematic exploration here. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively.

>>>>

### Interchangeability of mappings

@@

<!-- # how data looks -->
Smart meters provide large quantities of measurements on energy usage for households across Australia. One of the customer trial [@smart-meter] conducted as part of the Smart Grid Smart City (SGSC) project (2010-2014) in Newcastle, New South Wales and some parts of Sydney provides customer wise data on energy consumption in `general_supply_kwh` in every half hour from February 2012 to March 2014. \ref{tab:smart-meter} shows the data structure of the available data. It would be interesting to explore the energy consumption distribution for these customers and gain insights on their energy behavior which are lost either due to aggregation or looking only at coarser temporal units. The idea here is to show how looking at the energy consumption across different cyclic granularities together can help identify different behavioral patterns and identify the extreme and regular households.

@@

smart_meter %>% kable()
```

@@

R package **gravitas** [@R-gravitas] is used to facilitate the systematic exploration here. While trying to explore the energy behavior of these customers systematically across cyclic time granularities, the first thing we should have at our disposal is to know which all cyclic time granularities we can look at exhaustively.
